---
title: "Mediation analyses"
author: "Ryunosuke Goto"
date: "6/7/2022"
output: html_document
---

```{r setup, include=FALSE}

#to run RMD
#library(rmarkdown)
#rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]
#rmarkdown::render(paste(rootdir,"rmd/ses.Rmd", sep="/"))

knitr::opts_chunk$set(warning=FALSE, message=TRUE, echo=TRUE)

library(lfe)
library(stargazer)
library(knitr)
library(plm)
library(latex2exp)
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(kableExtra)
library(data.table) 
library(readxl)  
library(dplyr)
library(dotwhisker)
library(latex2exp)
library(parallel) 
library(geepack)
library(CMAverse)
library(ggpubr)
library(randomForest)
library(mlbench)
library(caret)
library(e1071)
library(missForest)
library(gtsummary)
library(knitr)
library(gt)
library(itertools)
library(missForest)
library(viridis)

detectCores()

rootdir <- system("git rev-parse --show-toplevel", intern=TRUE)[1]

source(paste(rootdir,"R/countyData.R",sep="/"))

options(timeout=2000)
sdf <- countyData(redo=FALSE) #set redo=TRUE to update

write.csv(sdf,paste(rootdir,"sdf.csv",sep="/"))

```


##Scatterplots of exposure, mediators, and outcome
```{r scatterplots, cache=FALSE, warning=FALSE, message=FALSE, echo=FALSE, results='hide', fig.width=15, fig.height=15}
#####scatterplots#####
#create dataset 
sdf_l <- subset(sdf, state %in% c("AL","AK","AZ","CA","CO","CT","DE",
                              "FL","GA","HI","ID","IL","IN","DC", 
                              "KS","KY","LA","ME","MD","MA","MI",
                              "MN","MT","MS","MO","NV","NH","NJ",
                              "NM","NY","NC","OH","OK","OR","PA",
                              "RI","SC","TN","TX","VA","VT","WA",
                              "WV","WI", #lockdown states
                              "AR","IA","NE","ND","SD","UT","WY" #no lockdown states
                              )) 

#pctPoverty and deaths
fig2  <-  ggpubr::ggscatter(data=sdf_l, x="pctPoverty",y="deaths_2021", fill="Black", color="Black",
                            xlab = "Poverty rate (%)\n", ylab = "COVID-19 deaths per 100,000 in 2021",
                           add = "reg.line", conf.int = TRUE, 
                           cor.coef = TRUE, cor.method = "pearson",
                           add.params = list(color = "grey45",fill = "grey45"),
                           cor.coeff.args = list(method = "pearson", label.x = 25, label.y = 750, size = 5)
                           ) 

#pctPoverty and Series_Complete_Pop_Pct
fig3  <-  ggpar(ggpubr::ggscatter(data=sdf_l, x="pctPoverty",y="Series_Complete_Pop_Pct", fill="Black", color="Black",
                            xlab = "Poverty rate (%)\n", ylab = "Proportion fully vaccinated \nby December 31, 2021 (%)",
                           add = "reg.line", conf.int = TRUE, 
                           cor.coef = TRUE, cor.method = "pearson",
                           add.params = list(color = "grey45",fill = "grey45"),
                           cor.coeff.args = list(method = "pearson", label.x = 17, label.y = 13, size = 5)
                           ) 
                #, ylim = c(0,110)
)

#Series_Complete_Pop_Pct and deaths
fig4  <-  ggpar(ggpubr::ggscatter(data=sdf_l, x="Series_Complete_Pop_Pct",y="deaths_2021", fill="Black", color="Black",
                            xlab = "Proportion fully vaccinated \nby December 31, 2021 (%)", ylab = "COVID-19 deaths per 100,000 in 2021",
                           add = "reg.line", conf.int = TRUE, 
                           cor.coef = TRUE, cor.method = "pearson",
                           add.params = list(color = "grey45",fill = "grey45"),
                           cor.coeff.args = list(method = "pearson", label.x = 35, label.y = 750, size = 5)
                           ) 
                #, ylim = c(0,1500)
)

max(sdf_l$deaths_2021, na.rm=TRUE)  
sdf_l[sdf_l$deaths_2021==max(sdf_l$deaths_2021, na.rm=TRUE),]$fips  
min(sdf_l$deaths_2021, na.rm=TRUE)
sdf_l[sdf_l$deaths_2021==min(sdf_l$deaths_2021, na.rm=TRUE),]$fips

max(sdf_l$pctPoverty, na.rm=TRUE)
sdf_l[sdf_l$pctPoverty==max(sdf_l$pctPoverty, na.rm=TRUE),]$fips
min(sdf_l$pctPoverty, na.rm=TRUE)
sdf_l[sdf_l$pctPoverty==min(sdf_l$pctPoverty, na.rm=TRUE),]$fips

max(sdf_l$Series_Complete_Pop_Pct, na.rm=TRUE)
sdf_l[sdf_l$Series_Complete_Pop_Pct==max(sdf_l$Series_Complete_Pop_Pct, na.rm=TRUE),]$fips
min(sdf_l$Series_Complete_Pop_Pct, na.rm=TRUE)
sdf_l[sdf_l$Series_Complete_Pop_Pct==min(sdf_l$Series_Complete_Pop_Pct, na.rm=TRUE),]$fips

pdf(sprintf("%s/figures/scatterplots.pdf",rootdir), width=8, height=8)
ggarrange(ggarrange(fig2, ncol = 1, labels = c("A")),        
          ggarrange(fig4, fig3, ncol = 2, labels = c("B", "C")), 
          nrow = 2                                   
          ) 
dev.off()

ggarrange(ggarrange(fig2, ncol = 1, labels = c("A")),        
          ggarrange(fig4, fig3, ncol = 2, labels = c("B", "C")), 
          nrow = 2                                   
          ) 

```


##Associations of exposure, mediators, and outcome
```{r regressions, cache=FALSE, warning=FALSE, message=FALSE, echo=FALSE, results='hide'}
#Variable selection
set.seed(123)
Y_2021 = "deaths_2021"
E = "pctPoverty"
M_vax = c(
  "Series_Complete_Pop_Pct"
)
C = c("PropMale",
      "PropAbove65",
      "no.college.diploma",
      "native",
      "asian",
      "black",
      "white",
      "hispanic",
      "state"
) 

d = sdf[c("fips",Y_2021,E,M_vax,C)]


createfmla <- function(yvar, xvars) {
  rhs <- paste(xvars, collapse=" + ")
  return(as.formula(paste(yvar, "~", rhs, sep=" ")))
}
createint <- function(Y,E,M) {
  list <- NULL
  for(i in 1:length(M)){
    list <- c(list,paste(E,M[i], sep="*"))
  }
  rhs <- paste(list, collapse=" + ")
  return(as.formula(paste(Y, "~", rhs, sep=" ")))
}

set.seed(123)


#create dataset
d_l <- subset(d, state %in% c("AL","AK","AZ","CA","CO","CT","DE",
                              "FL","GA","HI","ID","IL","IN","DC", 
                              "KS","KY","LA","ME","MD","MA","MI",
                              "MN","MT","MS","MO","NV","NH","NJ",
                              "NM","NY","NC","OH","OK","OR","PA",
                              "RI","SC","TN","TX","VA","VT","WA",
                              "WV","WI", #lockdown states
                              "AR","IA","NE","ND","SD","UT","WY" #no lockdown states
                              ))


#impute with RF
set.seed(123)
d_l_mf <- d_l
d_l_mf$state <- factor(d_l_mf$state)
d_l_mf <- subset(d_l_mf, select=-c(fips))
dimp <- missForest(xmis = d_l_mf, ntree=100, maxiter = 10, parallelize = 'no')
# dimp$OOBerror
# dimp$error
d_l_rf<-cbind(d_l$fips, dimp$ximp)


createfmla <- function(yvar, xvars) {
  rhs <- paste(xvars, collapse=" + ")
  return(as.formula(paste(yvar, "~", rhs, sep=" ")))
}


#Exposure-outcome association
reg_ye_2021 = glm(createfmla(Y_2021, c(E,C)), family = gaussian(link="identity"), data = d_l_rf)
reg_ye_2021.beta <- coef(reg_ye_2021)
reg_ye_2021.SE <- coef(summary(reg_ye_2021))[, 2]
reg_ye_2021.p <- coef(summary(reg_ye_2021))[, 4]
reg_ye_2021.lcl <- reg_ye_2021.beta - qnorm(0.975) * reg_ye_2021.SE
reg_ye_2021.ucl <- reg_ye_2021.beta + qnorm(0.975) * reg_ye_2021.SE

#Mediator-outcome association
reg_ym_vax = glm(createfmla(Y_2021, c(M_vax,C)), family = gaussian(link="identity"), data = d_l_rf)
reg_ym_vax.beta <- coef(reg_ym_vax)
reg_ym_vax.SE <- coef(summary(reg_ym_vax))[, 2]
reg_ym_vax.p <- coef(summary(reg_ym_vax))[, 4]
reg_ym_vax.lcl <- reg_ym_vax.beta - qnorm(0.975) * reg_ym_vax.SE
reg_ym_vax.ucl <- reg_ym_vax.beta + qnorm(0.975) * reg_ym_vax.SE


```

```{r}
#excess covid deaths per 100,000 (in 2021) for every 10% increase in poverty
kable(cbind(reg_ye_2021.beta,reg_ye_2021.lcl,reg_ye_2021.ucl,reg_ye_2021.p/10)[2,]*10)
#reduction in covid deaths per 100,000 (in 2021) for every 10% increase in vaccination rate
kable(cbind(reg_ym_vax.beta,reg_ym_vax.lcl,reg_ym_vax.ucl,reg_ym_vax.p/10)[2,]*10)
```


##US heatmap of exposure, mediators, and outcome
```{r maps, cache=FALSE, results='hide', echo=FALSE, fig.width=8, fig.height=20}
#####maps#####
f.map.deaths_2021 = usmap::plot_usmap(data = sdf_l, values = "deaths_2021",  color = "black", labels=FALSE, size=0.1) + 
  scale_fill_gradient2(low = "white", mid="red4", high = "black", midpoint = max(sdf_l$deaths_2021, na.rm=TRUE)/2, name = "", label = scales::comma) +
  labs(title="COVID-19 deaths per 100,000") +
  theme(plot.title = element_text(hjust = 0.5,size=16))

f.map.pov = usmap::plot_usmap(data = sdf_l, values = "pctPoverty",  color = "black", labels=FALSE, size=0.1) + 
  scale_fill_gradient2(low = "white", mid="blue4", high = "black", midpoint = max(sdf_l$pctPoverty, na.rm=TRUE)/2, name = "", label = scales::comma) +
  labs(title="Poverty rate (%)") +
  theme(plot.title = element_text(hjust = 0.5,size=16))

f.map.Series_Complete_Pop_Pct = usmap::plot_usmap(data = sdf_l, values = "Series_Complete_Pop_Pct",  color = "black", labels=FALSE, size=0.1) + 
  scale_fill_gradient2(low = "white", mid="chartreuse4", high = "black", midpoint = max(sdf_l$Series_Complete_Pop_Pct, na.rm=TRUE)/2, name = "", label = scales::comma) +
  labs(title="Proportion fully vaccinated by December 31, 2021 (%)") +
  theme(plot.title = element_text(hjust = 0.5,size=16))

pdf(sprintf("%s/figures/map.pdf",rootdir), width=8, height=20)
gridExtra::grid.arrange(f.map.deaths_2021,f.map.pov,f.map.Series_Complete_Pop_Pct,nrow=3)
dev.off()

gridExtra::grid.arrange(f.map.deaths_2021,f.map.pov,f.map.Series_Complete_Pop_Pct,nrow=3)
```


##Basic characteristics
```{r table, cache=FALSE, echo=FALSE}
#summary
sdf_l <- subset(sdf, state %in% c("AL","AK","AZ","CA","CO","CT","DE",
                              "FL","GA","HI","ID","IL","IN","DC", 
                              "KS","KY","LA","ME","MD","MA","MI",
                              "MN","MT","MS","MO","NV","NH","NJ",
                              "NM","NY","NC","OH","OK","OR","PA",
                              "RI","SC","TN","TX","VA","VT","WA",
                              "WV","WI", #lockdown states
                              "AR","IA","NE","ND","SD","UT","WY" #no lockdown states
                              )) 

results <- sdf_l %>% select(PropAbove65, PropMale, 
                          asian, hispanic, white, black, native,
                          pctPoverty, no.college.diploma,
                          Smokers_Percentage,DiabetesPercentage,obesity,
                          copd, hbp, chd, stroke,
                          Series_Complete_Pop_Pct,
                          deaths_2021)
tbl <- tbl_summary(results,
            statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} / {N} ({p}%)"),
            label = list(
              PropAbove65 ~ "Proportion aged 65+ years (%)", 
              PropMale ~ "Proportion of males (%)", 
              asian ~ "Proportion of Asians, Native Hawaiians, or other Pacific Islanders, non-Hispanic (%)", 
              hispanic ~ "Proportion of Hispanics (%)", 
              white ~ "Proportion of non-Hispanic Whites (%)", 
              black ~ "Proportion of non-Hispanic Blacks (%)", 
              native ~ "Proportion of American Indians/Alaska Natives, non-Hispanic (%)", 
              pctPoverty ~ "Proportion living in poverty (%)", 
              no.college.diploma ~ "Proportion without 4+ years of college education (%)", 
              Smokers_Percentage ~ "Proportion of smokers (%)", 
              DiabetesPercentage ~ "Proportion of adults with diabetes (%)", 
              obesity ~ "Proportion of obese adults (%)", 
              copd ~ "Proportion of adults with chronic obstructive pulmonary disease (%)", 
              hbp ~ "Proportion of adults with high blood pressure (%)", 
              chd ~ "Proportion of adults with coronary heart disease (%)", 
              stroke ~ "Proportion of adults with stroke (%)", 
              Series_Complete_Pop_Pct ~ "Percent fully vaccinated by December 31st, 2021 (%)",
              deaths_2021 ~ "COVID-19 deaths per 100,000 in April-December 2021"
              ),
            missing_text = "(Missing)",
            digits = list(
              PropAbove65 ~ c(1,1), 
              PropMale ~ c(1,1), 
              asian ~ c(1,1), 
              hispanic ~ c(1,1),  
              white ~ c(1,1),  
              black ~ c(1,1),  
              native ~ c(1,1), 
              pctPoverty ~ c(1,1), 
              no.college.diploma ~ c(1,1),  
              Smokers_Percentage ~ c(1,1),  
              DiabetesPercentage ~ c(1,1),  
              obesity ~ c(1,1), 
              copd ~ c(1,1), 
              hbp ~ c(1,1), 
              chd ~ c(1,1), 
              stroke ~ c(1,1),  
              Series_Complete_Pop_Pct ~ c(1,1),
              deaths_2021 ~ c(1,1)
              ),
            percent = NULL)

tbl %>%    
  as_gt() %>%            
  gt::gtsave(          
    filename = sprintf("%s/tables/basic_characteristics.html",rootdir)
  )

tbl %>%    
  as_gt()

```


##Mediation analysis of the SES-COVID-19 mortality association
###Outcome: COVID-19 death rates in 2021
###Mediators: vaccination rate up to December 31, 2021
```{r mediation for vaccination, cache=FALSE, warning=FALSE, message=FALSE, results='hide'}
#Variable selection
set.seed(123)
Y = "deaths_2021"
E = "pctPoverty"
M = c(
  "Series_Complete_Pop_Pct"
)
C = c("PropMale",
      "PropAbove65",
      "no.college.diploma",
      "native",
      "asian",
      "black",
      "white",
      "hispanic",
      "state"
) 

d = sdf[c("fips",Y,E,M,C)]

createfmla <- function(yvar, xvars) {
  rhs <- paste(xvars, collapse=" + ")
  return(as.formula(paste(yvar, "~", rhs, sep=" ")))
}
createint <- function(Y,E,M) {
  list <- NULL
  for(i in 1:length(M)){
    list <- c(list,paste(E,M[i], sep="*"))
  }
  rhs <- paste(list, collapse=" + ")
  return(as.formula(paste(Y, "~", rhs, sep=" ")))
}

set.seed(123)


#create dataset
d_l <- subset(d, state %in% c("AL","AK","AZ","CA","CO","CT","DE",
                              "FL","GA","HI","ID","IL","IN","DC", 
                              "KS","KY","LA","ME","MD","MA","MI",
                              "MN","MT","MS","MO","NV","NH","NJ",
                              "NM","NY","NC","OH","OK","OR","PA",
                              "RI","SC","TN","TX","VA","VT","WA",
                              "WV","WI", #lockdown states
                              "AR","IA","NE","ND","SD","UT","WY" #no lockdown states
                              ))

# max(d_l$Series_Complete_Pop_Pct,na.rm=TRUE)
# quantile(d_l$Series_Complete_Pop_Pct,0.90,na.rm=TRUE)
# quantile(d_l$Series_Complete_Pop_Pct,0.75,na.rm=TRUE)
# quantile(d_l$Series_Complete_Pop_Pct,0.50,na.rm=TRUE)

#impute with RF
set.seed(123)
d_l_mf <- d_l
d_l_mf$state <- factor(d_l_mf$state)
d_l_mf <- subset(d_l_mf, select=-c(fips))
dimp <- missForest(xmis = d_l_mf, ntree=100, maxiter = 10, parallelize = 'no')
# dimp$OOBerror
# dimp$error
d_l_rf<-cbind(d_l$fips, dimp$ximp)

createfmla <- function(yvar, xvars) {
  rhs <- paste(xvars, collapse=" + ")
  return(as.formula(paste(yvar, "~", rhs, sep=" ")))
}

set.seed(123)

#g-formula approach

#max values
mval.list <- list()

mval.list <- list(max(d_l$Series_Complete_Pop_Pct, na.rm=TRUE)) 
fit_l <- cmest(
  data=d_l_rf, model="gformula", 
  outcome = Y, exposure = E, mediator = M, basec = C, 
  yreg="linear", mreg=rep(list("linear"),length(M)),
  astar = median(d_l$pctPoverty, na.rm=TRUE), a = median(d_l$pctPoverty, na.rm=TRUE)+10, 
  EMint=TRUE,
  mval = mval.list,
  estimation = "imputation", multimp = FALSE,
  inference = "bootstrap", nboot = 1000)
res_mediation_max_vax <- data.frame(
  "Statistic" = c("Total effect", "Controlled direct effect", "Proportion eliminated"),
  "Effect" = 
    round(c(summary(fit_l)$effect.pe["te"],summary(fit_l)$effect.pe["cde"],summary(fit_l)$effect.pe["pe"]),2),
  "Lower CL" = 
    round(c(summary(fit_l)$effect.ci.low["te"],summary(fit_l)$effect.ci.low["cde"],summary(fit_l)$effect.ci.low["pe"]),2),
  "Upper CL" = 
    round(c(summary(fit_l)$effect.ci.high["te"],summary(fit_l)$effect.ci.high["cde"],summary(fit_l)$effect.ci.high["pe"]),2),
  "P-value" = 
    round(c(summary(fit_l)$effect.pval["te"],summary(fit_l)$effect.pval["cde"],summary(fit_l)$effect.pval["pe"]),3)
)

res_mediation_max_vax %>% 
  gt() %>%
  cols_label(
    Statistic = " ",
    Lower.CL = "Lower CL",
    Upper.CL = "Upper CL",
    P.value = "P-value"
  ) %>% gt::gtsave(          
    filename = sprintf("%s/tables/mediation_max_vax.html",rootdir))

#90th percentile
mval.list <- list()
mval.list <- list(quantile(d_l$Series_Complete_Pop_Pct,0.90,na.rm=TRUE))
fit_l <- cmest(
  data=d_l_rf, model="gformula", 
  outcome = Y, exposure = E, mediator = M, basec = C, 
  yreg="linear", mreg=rep(list("linear"),length(M)),
  astar = median(d_l$pctPoverty, na.rm=TRUE), a = median(d_l$pctPoverty, na.rm=TRUE)+10, 
  EMint=TRUE,
  mval = mval.list,
  estimation = "imputation", multimp = FALSE,
  inference = "bootstrap", nboot = 1000)
res_mediation_0.9_vax <- data.frame(
  "Statistic" = c("Total effect", "Controlled direct effect", "Proportion eliminated"),
  "Effect" = 
    round(c(summary(fit_l)$effect.pe["te"],summary(fit_l)$effect.pe["cde"],summary(fit_l)$effect.pe["pe"]),2),
  "Lower CL" = 
    round(c(summary(fit_l)$effect.ci.low["te"],summary(fit_l)$effect.ci.low["cde"],summary(fit_l)$effect.ci.low["pe"]),2),
  "Upper CL" = 
    round(c(summary(fit_l)$effect.ci.high["te"],summary(fit_l)$effect.ci.high["cde"],summary(fit_l)$effect.ci.high["pe"]),2),
  "P-value" = 
    round(c(summary(fit_l)$effect.pval["te"],summary(fit_l)$effect.pval["cde"],summary(fit_l)$effect.pval["pe"]),3)
)

res_mediation_0.9_vax %>% 
  gt() %>%
  cols_label(
    Statistic = " ",
    Lower.CL = "Lower CL",
    Upper.CL = "Upper CL",
    P.value = "P-value"
  ) %>% gt::gtsave(          
    filename = sprintf("%s/tables/mediation_0.9_vax.html",rootdir))

#75th percentile
mval.list <- list()
mval.list <- list(quantile(d_l$Series_Complete_Pop_Pct,0.75,na.rm=TRUE))
fit_l <- cmest(
  data=d_l_rf, model="gformula", 
  outcome = Y, exposure = E, mediator = M, basec = C, 
  yreg="linear", mreg=rep(list("linear"),length(M)),
  astar = median(d_l$pctPoverty, na.rm=TRUE), a = median(d_l$pctPoverty, na.rm=TRUE)+10, 
  EMint=TRUE,
  mval = mval.list,
  estimation = "imputation", multimp = FALSE,
  inference = "bootstrap", nboot = 1000)
res_mediation_0.75_vax <- data.frame(
  "Statistic" = c("Total effect", "Controlled direct effect", "Proportion eliminated"),
  "Effect" = 
    round(c(summary(fit_l)$effect.pe["te"],summary(fit_l)$effect.pe["cde"],summary(fit_l)$effect.pe["pe"]),2),
  "Lower CL" = 
    round(c(summary(fit_l)$effect.ci.low["te"],summary(fit_l)$effect.ci.low["cde"],summary(fit_l)$effect.ci.low["pe"]),2),
  "Upper CL" = 
    round(c(summary(fit_l)$effect.ci.high["te"],summary(fit_l)$effect.ci.high["cde"],summary(fit_l)$effect.ci.high["pe"]),2),
  "P-value" = 
    round(c(summary(fit_l)$effect.pval["te"],summary(fit_l)$effect.pval["cde"],summary(fit_l)$effect.pval["pe"]),3)
)

res_mediation_0.75_vax %>% 
  gt() %>%
  cols_label(
    Statistic = " ",
    Lower.CL = "Lower CL",
    Upper.CL = "Upper CL",
    P.value = "P-value"
  ) %>% gt::gtsave(          
    filename = sprintf("%s/tables/mediation_0.75_vax.html",rootdir))
```
```{r}
#Vaccination rate set to max
knitr::kable(res_mediation_max_vax)
#Vaccination rate set to 90th percentile
knitr::kable(res_mediation_0.9_vax)
#Vaccination rate set to 75th percentile
knitr::kable(res_mediation_0.75_vax)
```



##How much of the SES-COVID association is shifted southwest by setting vaccinations to the maximum observed value?
##PE and risk reduction in COVID-19 mortality for different values of the vaccination rate
###Does increasing the vaccination rate increase PE of the association between SES and COVID-19 mortality (attenuate health inequity) and reduce average COVID-19 mortality (improve population health)? 
###Outcome: COVID-19 death rates in 2021
###Mediator: vaccination rate up to December 31, 2021
```{r southwest_vax, cache=FALSE, results='hide', fig.width=6, fig.height=10}
###for each vax, obtain PE and risk reduction in COVID-19 deaths
#Variable selection
set.seed(123)
Y = "deaths_2021"
E = "pctPoverty"
M = c(
    "Series_Complete_Pop_Pct"
    )
C = c("PropMale",
    "PropAbove65",
    "no.college.diploma",
    "native",
    "asian",
    "black",
    "white",
    "hispanic",
    "state"
    ) 

d = sdf[c("fips",Y,E,M,C)]


createfmla <- function(yvar, xvars) {
  rhs <- paste(xvars, collapse=" + ")
  return(as.formula(paste(yvar, "~", rhs, sep=" ")))
}
createint <- function(Y,E,M) {
  list <- NULL
  for(i in 1:length(M)){
    list <- c(list,paste(E,M[i], sep="*"))
    }
  rhs <- paste(list, collapse=" + ")
  return(as.formula(paste(Y, "~", rhs, sep=" ")))
}

set.seed(123)


#create dataset
d_l <- subset(d, state %in% c("AL","AK","AZ","CA","CO","CT","DE",
                              "FL","GA","HI","ID","IL","IN","DC", 
                              "KS","KY","LA","ME","MD","MA","MI",
                              "MN","MT","MS","MO","NV","NH","NJ",
                              "NM","NY","NC","OH","OK","OR","PA",
                              "RI","SC","TN","TX","VA","VT","WA",
                              "WV","WI", #lockdown states
                              "AR","IA","NE","ND","SD","UT","WY" #no lockdown states
                              ))

#impute with RF
set.seed(123)
d_l_mf <- d_l
d_l_mf$state <- factor(d_l_mf$state)
d_l_mf <- subset(d_l_mf, select=-c(fips))
dimp <- missForest(xmis = d_l_mf, ntree=100, maxiter = 10, parallelize = 'no')
# dimp$OOBerror
# dimp$error
d_l_rf<-cbind(d_l$fips, dimp$ximp)

vax <- NULL
pe <- NULL
rd <- NULL
median_vax = median(d_l$Series_Complete_Pop_Pct, na.rm=TRUE)
max_vax = max(d_l$Series_Complete_Pop_Pct, na.rm=TRUE)
plot_vax <- NULL
n <- 1

for (j in seq(median_vax,max_vax,by=1)){ 
    mval.list_combined <- list()
    mval.list_combined <- list(j) 
    fit_l_combined <- cmest(
      data=d_l_rf, model="gformula", 
      outcome = Y, exposure = E, mediator = M, basec = C, 
      yreg="linear", mreg=rep(list("linear"),length(M)),
      astar = median(d_l$pctPoverty, na.rm=TRUE), a = median(d_l$pctPoverty, na.rm=TRUE)+10, 
      EMint=TRUE,
      mval = mval.list_combined,
      estimation = "imputation", multimp = FALSE,
      inference = "bootstrap", nboot = 1)
    vax[n] = j
    pe[n] = summary(fit_l_combined)[9]$effect.pe["pe"] * 100
        
    #create regression with E, M, C
    reg = glm(deaths_2021 ~ Series_Complete_Pop_Pct + pctPoverty + pctPoverty*Series_Complete_Pop_Pct + 
                PropMale + 
                PropAbove65 +
                no.college.diploma +
                native +
                asian +
                black +
                white +
                hispanic +
                state,
              family = gaussian(link="identity"), data = d_l_rf)
    
    d_l_mmax <- d_l_rf
    d_l_mmax$Series_Complete_Pop_Pct <- j
    
    #risk reduction (how many fewer deaths per 100,000 population with the specified mediator values?)
    rd[n] = -(mean(predict(reg, newdata=d_l_mmax)) - mean(d_l_mmax$deaths_2021))
    
    n <- n+1
}

#max risk reduction
-(mean(predict(reg, newdata=d_l_mmax)) - mean(d_l_mmax$deaths_2021))
t.test(d_l_mmax$deaths_2021, predict(reg, newdata=d_l_mmax), paired=TRUE)

plot_vax <- data.frame(pe, rd, vax)

fig_vax = ggplot(data = plot_vax, aes(x = pe,y = rd, color = vax)) + 
  geom_point(size = 3) +
  scale_x_continuous("Proportion eliminated of the poverty-COVID-19 death rate association (%)") +  
  scale_y_continuous("Average reduction in COVID-19 deaths per 100,000") +
  scale_color_gradient(low="blue", high="red") +
  labs(color="Vaccination \nrate (%)") +
  theme(legend.position = c(0.8, 0.3),legend.background = element_rect(fill="white",linetype="solid", color ="black")) 

#Variable selection
set.seed(123)
Y = "deaths_2021"
E = "pctPoverty"
M = c(
    "Series_Complete_Pop_Pct"
    )
C = c("PropMale",
    "PropAbove65",
    "no.college.diploma",
    "native",
    "asian",
    "black",
    "white",
    "hispanic",
    "state"
    ) 

d = sdf[c("fips",Y,E,M,C)]


createfmla <- function(yvar, xvars) {
  rhs <- paste(xvars, collapse=" + ")
  return(as.formula(paste(yvar, "~", rhs, sep=" ")))
}
createint <- function(Y,E,M) {
  list <- NULL
  for(i in 1:length(M)){
    list <- c(list,paste(E,M[i], sep="*"))
    }
  rhs <- paste(list, collapse=" + ")
  return(as.formula(paste(Y, "~", rhs, sep=" ")))
}

set.seed(123)


#create dataset
d_l <- subset(d, state %in% c("AL","AK","AZ","CA","CO","CT","DE",
                              "FL","GA","HI","ID","IL","IN","DC", 
                              "KS","KY","LA","ME","MD","MA","MI",
                              "MN","MT","MS","MO","NV","NH","NJ",
                              "NM","NY","NC","OH","OK","OR","PA",
                              "RI","SC","TN","TX","VA","VT","WA",
                              "WV","WI", #lockdown states
                              "AR","IA","NE","ND","SD","UT","WY" #no lockdown states
                              ))

#impute with RF
set.seed(123)
d_l_mf <- d_l
d_l_mf$state <- factor(d_l_mf$state)
d_l_mf <- subset(d_l_mf, select=-c(fips))
dimp <- missForest(xmis = d_l_mf, ntree=100, maxiter = 10, parallelize = 'no')
# dimp$OOBerror
# dimp$error
d_l_rf<-cbind(d_l$fips, dimp$ximp)

#the original association
reg = glm(createfmla(Y, E), family = gaussian(link="identity"), data = d_l_rf)
summary(reg)

#create regression with E, M, C, and predict Y with max vax
#with E-M interaction
reg = glm(deaths_2021 ~ pctPoverty + Series_Complete_Pop_Pct + pctPoverty*Series_Complete_Pop_Pct + 
            PropMale + 
            PropAbove65 +
            no.college.diploma +
            native +
            asian +
            black +
            white +
            hispanic +
            state,
          family = gaussian(link="identity"), data = d_l_rf)
d_l_mmax <- d_l_rf
d_l_mmax$Series_Complete_Pop_Pct <- max(d_l$Series_Complete_Pop_Pct,na.rm=TRUE)
d_l_mmax[Y] <- predict(reg, newdata=d_l_mmax)

#Regress with predicted Y
reg = glm(createfmla(Y, E), family = gaussian(link="identity"), data = d_l_mmax)
summary(reg)

#add to scatterplot
fig  <-  ggpubr::ggscatter(data=d_l, x="pctPoverty",y="deaths_2021", fill="grey45", color="grey45",
                            xlab = "Poverty rate (%)", ylab = "COVID-19 deaths per 100,000",
                            add = "reg.line", #conf.int = TRUE, 
                            #cor.coef = TRUE, 
                            cor.method = "pearson",
                            add.params = list(color = "Black",fill = "Black") 
) 
scatterplot_vax = 
  fig + 
    geom_segment(aes(x = min(d_l$pctPoverty, na.rm=TRUE), xend = max(d_l$pctPoverty, na.rm=TRUE), 
                     y = coef(reg)["(Intercept)"] + coef(reg)["pctPoverty"]*min(d_l$pctPoverty, na.rm=TRUE), 
                     yend = coef(reg)["(Intercept)"] + coef(reg)["pctPoverty"]*max(d_l$pctPoverty, na.rm=TRUE)),
                 color="red", lwd=1) + 
    xlim(min(d_l$pctPoverty, na.rm=TRUE), max(d_l$pctPoverty, na.rm=TRUE)) +
    annotate(geom="text", x=45, y=110, label="Vaccination rate \nmaximized", color="red") +
    annotate(geom="text", x=45, y=290, label="Observed \nvaccination rate", color="Black")


pdf(sprintf("%s/figures/southwest_vax.pdf",rootdir), width=6, height=10)
ggarrange(fig_vax, scatterplot_vax, ncol = 1, labels = c("A", "B"))
dev.off()

ggarrange(fig_vax, scatterplot_vax, ncol = 1, labels = c("A", "B"))
```
